Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-26 docs/paper.tex
Slightly modified use of references

	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.

@@

	In \cite{sharon2013}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work. These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents. If any such combination is found for a node, there is no need to search the $k$-agent MDD so the next ICT node can be considered. The three pruning methods are as follows.

@@

	The full ICTS algorithm including a pruning step as described above is given by Algorithm \ref{icts-algo}. It is reproduced from \cite{sharon2013} for completeness. In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2013} is that this often outperforms other variants.

@@

	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound. Lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}. As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.

>>>>

	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.

@@

	In addition to ID, three pruning methods can be used to speed up ICTS \cite{sharon2013}, two of which are used in this work. These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents. If any such combination is found for a node, there is no need to search the $k$-agent MDD so the next ICT node can be considered. The three pruning methods are as follows.

@@

	The full ICTS algorithm including a pruning step as described above is given by Algorithm \ref{icts-algo}. It is reproduced from \cite{sharon2013} for completeness. In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as this often outperforms other variants \cite{sharon2013}.

@@

	Another possibility would be to use the lower-bound on solution SIC to improve ICTS-m by only executing the $k$-agent low-level search for nodes that satisfy this bound. The lower-bounding in ICTS-m could then be further improved by finding the optimal SIC for the anonymous MAPF instance corresponding to each team using an approach similar to those described in \cite{baauw2021}. As long as there is a team that does not meet its bound, branching only on agents within this team is possible without losing optimality.
